### 2023-08-30 manuscript.tex
Re-wrote section on input genomes to include discussion of alternative splicing in response to reviewer comments

\subsection{Input genomes and pre-processing}
All annotated genomes in the genus \textit{Drosophila} available in April 2022 were downloaded from NCBI's RefSeq database. The assemblies annotated by the NCBI eukaryotic genome annotation pipeline have passed several quality checks and all have supporting transcript evidence, so the annotations are generally highly complete~\cite{Thibaud-Nissen2013}. The \textit{D. miranda} annotation was excluded due to its unusual karyotype~\cite{Dobzhansky1935}. Other annotations were excluded after preliminary clustering showed a deficiency in the number of orthologous groups containing those genomes, indicating their annotations were less complete (data not shown). The \textit{D. melanogaster} annotation was downloaded from FlyBase~\cite{Gramates2022}. In total, the input data consists of 33 genomes, which are listed in Table~\ref{stable:genomes}. Many genes have transcripts that differ only in their UTRs, and as a result there are many duplicate protein sequences in the annotations. Though not strictly necessary, we removed the duplicates in our pipeline, which greatly reduced the computational burden of later steps.

>>>>

\subsection{Input genomes and pre-processing}
All annotated genomes in the genus \textit{Drosophila} available in April 2022 were downloaded from NCBI's RefSeq database. The assemblies annotated by the NCBI eukaryotic genome annotation pipeline have passed several quality checks and all have supporting transcript evidence, so the annotations generally have highly complete gene sets as measured by BUSCO scores~\cite{Thibaud-Nissen2013, Simo2015}. The \textit{D. miranda} annotation was excluded due to its unusual karyotype~\cite{Dobzhansky1935}. Other annotations were excluded after preliminary clustering showed a deficiency in the number of orthologous groups containing those genomes, indicating their annotations were less complete (data not shown). The \textit{D. melanogaster} annotation was downloaded from FlyBase~\cite{Gramates2022}. In total, the input data consists of 33 genomes, which are listed in Table~\ref{stable:genomes}.

Many genes have transcripts that differ only in their UTRs, and as a result there are many duplicate protein sequences in the annotations. Though not strictly necessary, we removed the duplicates in our pipeline, which greatly reduced the computational burden of later steps. However, we included all isoforms with distinct sequences for each gene in the subsequent BLAST searches. This differs from many orthology inference pipelines that select a representative sequence for each gene at the onset, typically the longest in practice. We took this approach to avoid arbitrarily choosing representative sequences for genes, which may result in alignment artifacts if the sequences are derived from transcripts with different intron-exon structures. Furthermore, it also allowed us to to leverage the results of the initial clustering and alignment steps to make more informed choices of representative sequences, as discussed in subsequent sections.
